---
title: "mlr fits and condvis2"
author: "Catherine B. Hurley"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mlr fits and condvis2}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=5, fig.height=5 ,fig.align="center"
)
fpath <- "vignettefigs/"
```

`mlr` is a R package that offers
a unified interface to machine learning models. 
By writing an interface between `condvis2` and `mlr` a vast number
of machine learning fits may be explored with `condvis`.
Presently, regression, classification and clustering varieties of `mlr` learners
work with `condvis'.

A list of models supported by `parsnip`mlr` is found on this link:
<https://mlr.mlr-org.com/articles/tutorial/integrated_learners.html>

## Regression

Set up the task, learner and train the model.
```{r eval=F}
library(mlr)
library(MASS)
library(condvis2)
Boston1 <- Boston[,9:14]

rtask <- makeRegrTask(id = "bh", data = Boston1, target = "medv")
rmod <- train(makeLearner("regr.lm"), rtask)
rmod1 <- train(makeLearner("regr.fnn"), rtask)
```

Use condvis to explore the models:
```{r eval=F}
condvis(Boston1, model=list(rmod,rmod1), response="medv", sectionvars="lstat")
```
Choose tour "Diff fits" to explore differences between the fits


Some tasks, for example linear regression, support standard errors and so confidence intervals.
This option needs to be added to `makeLearner`.
Then, tell `condvis` to plot an interval using `pinterval="confidence` for that fit.

```{r eval=F}
rmod <- train(makeLearner("regr.lm", predict.type="se"), rtask)
condvis(Boston1, model=rmod, response="medv", sectionvars="lstat", predictArgs=list(list(pinterval="confidence")))
```



## Classification

Set up the task, learner and train the model.
```{r eval=F}
cltask = makeClassifTask(data = iris, target = "Species")
cllrn = makeLearner("classif.lda",predict.type = "prob") # need predict.type ="probs" to get probs
clmod = train(cllrn, cltask)
```
Explore with `condvis`:
```{r eval=F}
condvis(iris, model=clmod, response="Species", sectionvars=c("Petal.Length", "Petal.Width"), pointColor="Species")
```
Click on "Show probs" to see class probabilities.

## Clustering


```{r eval=F}

ctask = makeClusterTask(data = iris[,-5])
clrn = makeLearner("cluster.kmeans") 
cmod = train(clrn, ctask)
```

Add the predicted class to the data to act as the response:

```{r eval=F}
library(dplyr)
iris1 <- iris

iris1$pclass <- cmod %>%
  predict(newdata=iris[,-5]) %>%
  getPredictionResponse() %>% 
    as.factor()

```

```{r eval=F}
condvis(data = iris1, model = cmod, 
        response="pclass",
        sectionvars=c("Petal.Length", "Petal.Width"), 
        conditionvars=c("Sepal.Length", "Sepal.Width"),pointColor="Species"
)

```




